### 2014-03-08 paper/designspace.tex
more text, more and more and more

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.png}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.  Darker grey is output.  Lighter grey is input.  \valkyrie{I don't know what else might go in the blank spaces... looking for suggestions!  Also, I'm not confident this breakdown is the most clear: for example, the "liquids" category includes the copper paint, which functions as wires ("threadables"), but takes the form of a liquid...  and the general presentation of the table could probably be better in some way.}}
\label{fig:designspace}
\end{figure*}

@@

Sensing via traditional electronic components (e.g., potentiometers, alcohol gas sensors) can be accomplished by conductive inserted media.  Components can be recessed into a print's surface, with their leads implanted into open tubes.  By inserting liquid copper paint instead of threading traditional wires, all components in a model can share a ground line, and the paint's drying process obviates the use of solder or glue to affix the components in place (see Figure \ref{fig:embeddedcomponents}).

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This sphere has a recessed space to hold a potentiometer.  The potentiometer and the LEDs share a ground, seen by the translucent rendered view in (b).}
\label{fig:embeddedcomponents}
\end{figure}

>>>>

\begin{figure*}[t]
\centering
    \includegraphics[width=\textwidth]{figures/designspace.png}
\caption{The design space of tube-based interactions.  Existing systems are written in regular font.  Those created with fabrication are in {\color{blue}blue}. In \emph{{\color{red}red italic}} are unexplored interactions creatable with custom-fabricated tubes.  Darker grey is output.  Lighter grey is input.  \valkyrie{I don't know what else might go in the blank spaces... looking for suggestions!  Also, I'm not confident this breakdown is the most clear: for example, the "liquids" category includes the copper paint, which functions as wires ("threadables"), but takes the form of a liquid...  and the general presentation of the table could probably be better in some way.  also, hello, make this wayyyyyy smaller.}}
\label{fig:designspace}
\end{figure*}

@@

Sensing via traditional electronic components (e.g., potentiometers, alcohol gas sensors) can be accomplished by conductive inserted media.  Components can be recessed into a print's surface, with their leads implanted into open tubes.  By inserting liquid copper paint instead of threading traditional wires, all components in a model can share a ground line, and the paint's drying process obviates the use of solder or glue to affix the components in place (see Figure \ref{fig:radio}).

### 2014-03-08 paper/exampleobjects.tex
more text, more and more and more

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toy}
\end{figure}

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toy}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.  These devices were all fabricated on a Makerbot Replicator 2.

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

We created a set of touch-sensitive toys and a companion app, reminiscent of the boat application in \cite{Harrison-acoustic}.  The brain, rabbit, and boat each have several distinct touch points on their surfaces.  These touch points are connected by an interior star topology of tubes filled with conductive copper paint, and touch sensing is performed via a single wire and SFCS (see Figure \ref{fig:toys}).  We built a smart base which can distinguish between the toys and also determine which toy is mounted: since each toy and each gesture has a distinct capacitive signature, we use a simple classifier trained to detect both toy and gesture based on profile.  These devices were all fabricated on a Makerbot Replicator 2.

### 2014-03-08 paper/tubes.tex
more text, more and more and more

Our tool creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

@@

Focus on shape of points and location of points.

Our basic first-pass routing algorithm uses the A* routing algorithm \cite{Hart-Astar}.  The path cost in our implementation is based only on shortest distance between the starting and ending points, without weighting for distance from the surface.

@@

A user can import a vector graphics file (such as SVG) describing the path she desires for her tubes.  We create a graph based on this input data, then add edges to make it connected and semi-Eulerian.  We create an Euler tour on the graph, and then thicken the path to create tubes.  Templates are used to resolve tube crossings in the plane.

@@

\begin{theorem}
 $G' = (V, E')$ is a connected, semi-Eulerian graph for which $E \subseteq E'$.
\end{theorem}
\begin{proof}
$E \subseteq E'$ : we never remove edges from $E$ in our algorithm.  $\therefore E \subseteq E'$.

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  An Euler tour is a path that touches every edge once, beginning and ending at the two nodes of odd degree: in this case, those are the user-selected start and end nodes.  We use a sligh modification of Fleury's algorithm\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this, where instead of randomly selecting from non-bridge paths at each node, we select the path which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.

@@

How we actually cut stuff and make tubes happen. \valkyrie{Ryan?}

@@

>>>>

To create tubes in which the location and shape of exterior connection points matters, we first allow users to select the connection points on the mesh's surface using a brush. Our tool then creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

@@

Our basic first-pass routing algorithm uses the A* routing algorithm \cite{Hart-Astar}.  The path cost in our implementation is based only on shortest distance between the starting and ending points, without weighting for distance from the surface.  We only permit the routing within the voxel grid of the mesh: i.e., the routing is not permitted to traverse through space outside the mesh itself.

Given this initial routing, we create a rod of slightly longer proportional length.  The rod must be longer, as the A* routing can follow the mesh boundaries and the rod requires extra length to be pushed away from the mesh surface.  While we do not have a theoretical basis for this proportional increase, \valkyrie{yet.  what might it be related to?  we can test how much of the A* path is outside the model, and how much is inside; further we can consider the distance from the A* path that is outside the model to the surface.  I think there's a good way to do this.  It might even just mean iteratively changing the rod length until we get something reasonably short and also smooth.  we can also return to the A* that I wrote which finds a routing through the mesh that respects its boundaries; this would get us closer to what we need for length in the first place.}, we have found 1.15 to be a reasonable multiplier in practice.  A too-long rod is forced to kink and expand further than necessary inside the model, while a too-short rod must be stretched, leading to non-smooth bending.

@@

A user can import a vector graphics file (such as SVG) describing the path she desires for her tubes.  We create a graph based on this input data, then add edges to make it connected and semi-Eulerian.  We create an Euler tour on the modified graph, and thicken the path to create tubes.  3D templates are used to resolve tube crossings in the plane.

@@

\valkyrie{does the proof of this theorem belong in the paper, or in the appendix?  we can push it back there if need be, although it's not super long.}
\begin{theorem}
 $G' = (V, E')$ is a connected, semi-Eulerian graph for which $E \subseteq E'$. \valkyrie{why is there such a huge space after this paragraph?}
\end{theorem}
\begin{proof}
$E \subseteq E'$ : we never remove edges from $E$ in our algorithm.  $\therefore E \subseteq E'$.

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  An Euler tour is a path that touches every edge once, beginning and ending at the two nodes of odd degree: in this case, those are the user-selected start and end nodes.  We use a weighted modification of Fleury's algorithm\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this, where instead of randomly selecting from non-bridge paths at each node, we select the path which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{When edges intersect in the plane (a), we match them to the nearest of our several intersection templates (b) to create 3D paths that do not interfere with each other.}
\label{fig:templates}
\end{figure}

\subsubsection{Edges that Intersect in the Plane}
Once we have a tour, we must resolve tubes that intersect in the plane.  Because we have a 3-dimensional canvas in which to work, we can push overlapping paths into the third dimension.

To detect intersecting edges, we \valkyrie{I'm not sure what we do.}.  We also consider edges at nodes with degree $>2$, as these edges are considered to cross.  When intersections have been detected, we match one of several templates to the affected edges (see Figure \ref{fig:templates}) using a nearest neighbors technique.  Our templates are parameterized, so the templates can be modified to accommodate precise intersection characteristics.

@@

How we actually cut stuff and make tubes happen. \valkyrie{Ryan?}  We have to actually respect whatever shapes people drew on the surface in the case of the exterior connection tubes (I mean, ideally, we would do a loft operation here).

@@

\valkyrie{this section may not be at all important.  I was thinking to use it to talk about different ways you can actually build the tubed things, and also constraints set down by the Makerbot vs. the Objet, but maybe that discussion is best made really short and moved to elsewhere}
